---
title: "P8105 Homework 5"
author: "Hyun Kim (hk3373)"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

theme_set(theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5)))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
```

# Problem 1

## Function to randomly draw birthday, check duplicates and return true or false
```{r define_birthday_funtion}
sim_birthday = function(n) {

  birthdays = sample(1:365, size = n, replace = TRUE)
  duplicate = length(unique(birthdays)) < n
  
  return(duplicate)
  
}
```

## Run function 10000 times for each group size between 2 and 50
```{r birthday_simulation}
sim_birthday_results = 
  expand_grid(n = 2:50,
              iter = 1:10000) |> 
  mutate(birthday_result = map_lgl(n, sim_birthday)) |> 
  group_by(n) |> 
  summarize(probability = mean(birthday_result))
```

## Plot the probability as a function of group size
```{r birthday_vs_probability}
sim_birthday_results |> 
  ggplot(aes(x = n, y = probability)) + 
  geom_line()
```

Group size and the probability that at least two people in group will share a 
birthday shows a positive relationship. As the group size increases, the 
probability also increases, approaching the value of 1. 
